Empirical normative theories

### 2020-06-22 simple.tex
Simpler defs of attack…

Given $\phi \in \Phi$, define ${\ibeatse[!\phi]} \subseteq (\allhist × \allargs) × \allargs$ such that $(\hist, \ar_1) \ibeatse[!\phi] \ar_0$ iff $[(\hist \ileadstoe ¬\phi) \lor (\hist \nileadstoe \phi)] \land [\hist \text{ ends with } \set{\ar_1, \ar_0}]$.
I also write that $\ar_1 \ibeatse[!\phi] \ar_0$ iff $\exists \hist \in \allhist \suchthat (\hist, \ar_1) \ibeatse[!\phi] \ar_0$, and $\hist \ibeatse[!\phi] \ar_0$ iff $[(\hist \ileadstoe ¬\phi) \lor (\hist \nileadstoe \phi)] \land [(\exists \ar_1 \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}) \lor (\hist = \set{\ar_0})]$.

Given any $\hist \in \allhist, \ar_0 \in \allargs, \phi \in \Phi$, define $(\hist, \ar_0) \ileadstost[i] \phi$ iff $\forall \ar_1 \in \allargs: (\hist, \ar_0) \nileadstoe[i] ¬\phi \land (\hist, \ar_0) \ileadstoe[i] \phi \land (\hist, \ar_0, \ar_1) \nileadstoe[i] ¬\phi \land (\hist, \ar_0, \ar_1) \ileadstoe[i] \phi$. 
Define $(\hist, \ar_0) \ileadstosts \phi$ iff $[(\hist, \ar_0) \ileadstost \phi] \land [\phi = \propsure ⇒ (\hist, \ar_0) \ileadstost \propposs]$.
Define $\ar_0 \ileadstost[i] \phi$ iff $\forall \hist \in \allhist, (\hist, \ar_0) \ileadstost[i] \phi$, and define similarly $\ar \ileadstosts \phi$ iff $\forall \hist \in \allhist, (\hist, \ar_0) \ileadstosts \phi$.
Note in particular that: 
\begin{equation}
	\label{eq:st-in-terms-of-e}
	\ar_0 \ileadstosts \phi ⇔ [\forall \ar_1: \ar_1 \nibeatse[!\phi] \ar_0] \land [\ar_0 \nileadstoe ¬\phi] \land [\ar_0 \ileadstoe \phi].
\end{equation}
\footnote{TODO Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$. Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$. Then, $(\ar', \ar) \ileadstost (\prop, \text{sure})$ iff she always chooses $\set{\prop}$ and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ iff she always chooses either $\set{\prop}$ or $\set{\prop, ¬\prop}$.}

@@

@@

>>>>

Given $\phi \in \Phi$ and $\hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadstoe \phi \land \hist \nileadstoe ¬\phi$.
Define $\hist \ileadstosts \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
Define $\ar \ileadstosts \phi$ iff $\forall \hist \in \allhist \suchthat \hist \text{ has } \ar \text{ as last or before last position }: \hist \ileadstosts \phi$.
\footnote{TODO Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$. Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$. Then, $(\ar', \ar) \ileadstost (\prop, \text{sure})$ iff she always chooses $\set{\prop}$ and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ iff she always chooses either $\set{\prop}$ or $\set{\prop, ¬\prop}$.}

@@

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatse[!\phi] \ar_0$ iff $\exists \hist \in \allhist \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0} \land \hist \nileadstosts \phi$.

\begin{proposition}
	$\forall i \in I, \phi \in \Phi, \ar_0 \in \allargs$:
\begin{equation}
	\label{eq:st-in-terms-of-e}
	\ar_0 \nileadstosts \phi ⇔ [\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar_0].
\end{equation}
\end{proposition}
\begin{proof}
	By definition of ${\ileadstosts}$, $\ar_0 \ileadstosts \phi ⇔ \forall \hist \in \allhist \suchthat [\exists \ar_1 \in \allargs \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}]: \hist \ileadstosts \phi.$ Equivalently, $\ar_0 \nileadstosts \phi ⇔ \exists \hist \in \allhist \suchthat [\exists \ar_1 \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0}] \land \hist \nileadstosts \phi$. This is also equivalent to $\ar_0 \nileadstosts \phi ⇔ \exists \hist \in \allhist, \ar_1 \in \allargs \suchthat \hist \text{ ends with } \set{\ar_1, \ar_0} \land \hist \nileadstosts \phi$. By definition of ${\ibeatse}$, this is the proposition to be proven.
\end{proof}

@@

I also write that $\hist \ibeatse[!\phi] \ar_0$ iff $\exists \ar_1 \in \allargs \suchthat (\hist \text{ ends with } \set{\ar_1, \ar_0}) \land (\ar_1 \ibeatse[!\phi] \ar_0)$.
